### 2014-02-27 paper/concrete.tex
Begin portage.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@

\begin{definition}[Inclusion of information-flow control languages]
    A language $(|tC|, |tC|^*, \tar{|V|}, \tar{|.->|}, \tar{|erasef l|})$ is
    included in $(|iC|, |iC|^*, \ifc{|V|}, \ifc{|.->|}, \ifc{|erasef
    l|})$ if there exists a total function $f : |tC -> iC|$ such that
    $f$ is a bijection over $l$-equivalences ($|tc|\ \tar{\approx_l}\
    |tc'|$ if and only if $f(|tc|)\ \ifc{\approx_l}\ f(|tc'|)$),
    preserves values (if $|tc| \subseteq \tar{|V|}$ then $|ic| \subseteq
    \ifc{|V|}$) and is functorial over $|.->|$ (if $|tc|\ \tar{|.->|}\
    |tc'|$ then $f(|tc|)\ \ifc{|.->|}\ f(|tc'|)$).
\end{definition}

\begin{theorem}[Isomorphism preserves termination insensitive non-interference]
    If \tar{L} is included in \ifc{L}, and \ifc{L} satisfies TINI, then
    \tar{L} satisfies TINI.
\end{theorem}

\begin{proof}
    Shown by transporting configurations and reduction derivations
    from \tar{L} to \ifc{L}, applying TINI and transporting the resulting
    equivalence back using bijectivity of $f$ over $l$-equivalences.
\end{proof}

@@

\begin{definition}[Isomorphism of information-flow control languages]
    A language $(|tC|, |tC|^*, \tar{|.->|}, \tar{|erasef l|})$ is
    isomorphic to \ifc{L} $(|iC|, |iC|^*, \ifc{|.->|}, \ifc{|erasef l|})$ are isomorphic if there exist total functions
    $f : |tC -> iC|$ and $f^{-1} : |iC -> tC|$ such that $f \circ f^{-1}
    = id_{|tC|}$, $f^{-1} \circ f = id_{|iC|}$, and $f$ and $f^{-1}$ are
    functorial over both $l$-equivalences (if $|tc|\ \tar{\approx_l}\
    |tc'|$ then $f(|tc|)\ \ifc{\approx_l}\ f(|tc'|)$ and vice-versa) and
    $|.->|$ (if $|tc|\ \tar{|.->|}\ |tc'|$ then $f(|tc|)\ \ifc{|.->|}\ f(|tc'|)$ and vice versa).
\end{definition}

@@

\begin{proof}
    Shown by transporting configurations and reduction derivations from
    \tar{L} to \ifc{L}, applying TSNI, and then transporting the
    resulting configuration and multi-step derivation back.
\end{proof}

>>>>

%{
%format tyerase c = "\varepsilon("c")"
%format tyerasef = "\varepsilon"
%format ^ = " "
%format c = "c"
%format c'
%format cc = "\con{"c"}"
%format cc'
%format ac = "\abs{"c"}"
%format ac'
%format V = "V"
%format cV = "\con{"V"}"
%format aV = "\abs{"V"}"
%format ~= = "\approx_l"
%format clequiv = "\con{"~="}"
%format alequiv = "\abs{"~="}"
%format creduce = "\con{".->"}"
%format areduce = "\abs{".->"}"
%format creducestar = "\con{".=>"}"
%format areducestar = "\abs{".=>"}"
%format (ap (f) (x)) = f"("x")"

\begin{definition}[Information-flow control language]
    An information-flow control language L is a tuple |(C, .->,
    erasef l)|, where $c \in |C|$ is the type of machine configurations, |.->| is a
    reduction relation between machine configurations and |erasef l : C .-> tyerase C|
    is an erasure function parametrized on labels from machine configurations to \emph{erased} machine
    configurations |tyerase C|.  For sequential languages, the
    language is augmented with a set of terminal configuration states $V
    \subseteq |C|$ for which there are no possible further transitions.
\end{definition}

\begin{definition}[$l$-equivalence]
    In a language |(C, .->, erasef l)|, two machine configurations
    $|memberf (c, c') C|$ are considered $l$-equivalent (|c ~= c'|)
    if |erase l c = erase l c'|.
\end{definition}

\newcommand{\con}[1]{\ensuremath{{\color{red} #1}}}
\newcommand{\abs}[1]{\ensuremath{{\color{blue} #1}}}

@@

\begin{definition}[Inclusion of information-flow control languages]
    A language \con{|(C, Ce, V, .->, erasef l)|} is included in another
    language \abs{|(C, Ce, V, .->, erasef l)|} if there exists a total function |f : tC -> iC| such that
    |f| is a bijection over |l|-equivalences (|cc clequiv cc'| if and only if
    |(ap f cc) alequiv (ap f cc')|),
    preserves values (if |subseteq cc cV| then |subseteq (ap f cc) aV|) and is
    functorial over |.=>| (if
    |cc creducestar cc'| then |(ap f cc) areducestar (ap f cc')|).
\end{definition}

\begin{theorem}[Isomorphism preserves termination insensitive non-interference]
    If a language \con{L} is included in a language \abs{L}, and \abs{L}
    satisfies TINI, then \con{L} satisfies TINI.
\end{theorem}

\begin{proof}
    Shown by transporting configurations and reduction derivations
    from \con{L} to \abs{L}, applying TINI and transporting the resulting
    equivalence back using bijectivity of $f$ over $l$-equivalences.
\end{proof}

@@

\begin{definition}[Isomorphism of information-flow control languages]
    A language $(|tC|, |tC|^*, \tar{|.->|}, \tar{|erasef l|})$ is
    isomorphic to \ifc{L} $(|iC|, |iC|^*, \ifc{|.->|}, \ifc{|erasef l|})$ are isomorphic if there exist total functions
    $f : |tC -> iC|$ and $f^{-1} : |iC -> tC|$ such that $f \circ f^{-1}
    = id_{|tC|}$, $f^{-1} \circ f = id_{|iC|}$, and $f$ and $f^{-1}$ are
    functorial over both $l$-equivalences (if $|tc|\ \tar{\approx_l}\
    |tc'|$ then $f(|tc|)\ \ifc{\approx_l}\ f(|tc'|)$ and if $|ic|\ \ifc{\approx_l}\ |ic'|$ then $f^{-1}$) and
    $|.->|$ (if $|tc|\ \tar{|.->|}\ |tc'|$ then $f(|tc|)\ \ifc{|.->|}\ f(|tc'|)$ and vice versa).
\end{definition}

@@

\begin{proof}
    Shown by transporting configurations and reduction derivations from
    \tar{L} to \ifc{L}, applying TSNI, and then transporting the
    resulting configuration and multi-step derivation back.
\end{proof}
%}
